---
title: "World's Dempgraphic Trends"
author: "Ketan"
date: "9 June 2018"
output: html_document
---

#Project to Analyze World's Demographic Trends

###Loading the required library

```{r, warning=FALSE}
library(ggplot2)
```

###Reading the Data

```{r}
stats <- read.csv("DemographicData.csv")
```

###Exploring the DataSet
```{r}
#Looking at the structure of the Data
str(stats)

#First Six Observations
head(stats)

#Last Six Observations
tail(stats)

#Summary of dataset
summary(stats)

#The Countries where birth rate is greater than 40 and internet users are less than 2%
stats[stats$Birth.rate > 40 & stats$Internet.users <2,]
```
**Comments : Out of 195 Countries only 3 Coutnries have birth rate more than 40 and internet users less than 2%.**

###Visualizing the DataSet (I)

**Comments : Creating the scatterplot to illustrate Birth Rate and Internet Usage statistics by Country and categorised by Countries' Income Groups**

```{r}
qplot(data=stats,x= Internet.users, y = Birth.rate, color = Income.Group,size=I(2),
      main="Birth Rate Vs Internet Users")
```

**Comments : From above scatterplot , it is found that the if internet access among people is more then birth rate tends to low **

###Creating Dataframe
```{r}
source("CountryRegionVectors.R")
my_df <- data.frame(Countries_2012_Dataset,Codes_2012_Dataset,Regions_2012_Dataset)
head(my_df)

#Changing the names of the Columns
colnames(my_df) <- c("Country","Code","Region")
head(my_df)

#Merging the Dataframes
head(stats)
merged <- merge(stats,my_df,by.x = "Country.Code",by.y= "Code")
head(merged)

merged$Country <- NULL
str(merged)

```
###Visualizing the DataSet (II)

**Comments : Creating the scatterplot to illustrate Birth Rate and Internet Usage statistics by Country and categorised by Countries' Region**

```{r}
qplot(data=merged,x= Internet.users, y = Birth.rate, color = Region,size=I(2),
      shape=I(17),alpha = I(0.7),
      main="Birth Rate Vs Internet Users")
```

**Comments : From above scatterplot , it is found that the African use less Internet and their birth rate is high, while in case of Europe the birth rate is quite low and internet users are in large amount. **