---
title: "World's Dempgraphic Trends"
author: "Ketan"
date: "9 June 2018"
output: html_document
---

#Project to Analyze World's Demographic Trends

###Loading the required library

```{r, warning=FALSE}
library(ggplot2)
```

###Reading the Data

```{r}
stats <- read.csv("DemographicData.csv")
```

###Exploring the DataSet
```{r}
#Looking at the structure of the Data
str(stats)

#First Six Observations
head(stats)

#Last Six Observations
tail(stats)

#Summary of dataset
summary(stats)

#The Countries where birth rate is greater than 40 and internet users are less than 2%
stats[stats$Birth.rate > 40 & stats$Internet.users <2,]
```
**Comments : Out of 195 Countries only 3 Coutnries have birth rate more than 40 and internet users less than 2%.**

###Visualizing the DataSet

```{r}
qplot(data=stats,x= Internet.users, y = Birth.rate, color = Income.Group,size=I(2))
```

**Comments : After creating the above scatterplot for all countries (By categorizing into them into different income groups) , it is found that the if internet access among people is more then birth rate would be low **